---
output: 
  md_document:
    variant: gfm
html_preview: TRUE
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

#  UltraPseR: Wappers for UltraPse in R

An R package for biological sequence representations 

- [UltraPse](https://github.com/pufengdu/UltraPse) by [pudengdu](https://github.com/pufengdu)

##  Install development vertion

~~!!!NOTE: We have tested these codes on Ubuntu 18.04.2 LTS. There is no guarantee that these codes can be compiled and executed on other platforms without modifications.(Currently cannot be installed in the **Win**)~~
Now, `UltraPseR` support all platforms.


The development version from github:

```{r eval=F}
if (!requireNamespace("devtools", quietly=TRUE))
    install.packages("devtools")
devtools::install_github("YuLab-SMU/UltraPseR")
```

##  Quick Example 

###  Calculated Component

```{r message=FALSE}
library(dplyr)
```

```{r}
tiny_sequences <- system.file("extdata", "tiny.fas", package = "UltraPseR")
x <- UltraPseR::UpseR(input = tiny_sequences, module = "comp", note = "stdprot") 
x
```

###  Pse-Protein

```{r fig.height = 2.5, fig.width = 11, message=FALSE, warning=FALSE, dpi=300}
tiny_sequences <- system.file("extdata", "tiny.fas", package = "UltraPseR")
pro <- UltraPseR::UpseR(input = tiny_sequences, note = "stdprot", module = "pse", property = "ZIMJ680105", w = 0.05, l = 10, t = 2)
p <- UltraPseR::plot_upse(pro)
p
```

###  Pse-DiDNA

```{r fig.height = 2.5, fig.width = 11, message=FALSE, warning=FALSE, dpi=300}
DNA_sequences <- system.file("extdata", "tiny-dna.fas", package = "UltraPseR")
dna_res <-UltraPseR::UpseR(input = DNA_sequences, note = "didna", module = "pse", property = "DD0033", w = 0.05, l = 3, t = 1)
p1 <- UltraPseR::plot_upse(dna_res)
p1
```

###  Explore proprety
```{r }
UltraPseR::available_prop(note = "didna")
```





